% Appendix A

\chapter{Frequently Asked Questions} % Main appendix title

\label{FAQ} % For referencing this appendix elsewhere, use \ref{AppendixA}

\paragraph{Why did you choose the top 60 apps in each category?}

When the 'top bestselling' category is selected, the page that loads shows the top 60 applications by default. Hence, it was chosen for convenience and the fact that Google made it 60 might have some meaning behind it.\\

\paragraph{Why Android 5.0 Lollipop OS?}

At the point of starting the project in 2017, Android 5.0/5.1 was the most widely used OS version. Moreover, currently over half the market uses Android 5.1 and below \cite{android2018version}.\\

\paragraph{Why did you select those categories?}

The categories are selected completely at random using a pseudo-random number generator in Python. Each category is sorted alphabetically and the minimum and maximum indexes are used as ranges for the python script, which produces a random number used to select each category.

\paragraph{Why only the Japan Playstore?}

Most analysis have been done on the global Playstore market or the one in the USA. Very few analysis have been done specifically for the Japan Playstore.

\paragraph{What was your budget?}

As for the budget, I have none so I only focused on the free apps.

\paragraph{Have you considered about the In-App Purchase Contents?}

Having a paid IAP rigged with malware would completely circumvent my detection method. 

\paragraph{Why is it only restricted to apps with a server connection?}

I feel that is it an important research as this type of malware involves the most damaging type of privacy violation as it sends the information to a third party.





