% Appendix A

\chapter{Glossary} % Main appendix title

\label{Glossary} % For referencing this appendix elsewhere, use \ref{AppendixA}

\noindent \textbf{barriers to entry} are the costs or other obstacles that prevent new competitors from easily entering an industry or area of business. \footnote{definition taken from Investopedia article 'Barriers to Entry', retrieved on 2018-07-18.}

\noindent \textbf{botnet} is a number of Internet-connected devices, each of which is running one or more bots. \footnote{definition taken from Wikipedia article 'Botnet', retrieved on 2018-07-18.}

\noindent \textbf{bots} is a device or piece of software that can execute commands, reply to messages, or perform routine tasks, as online searches, either automatically or with minimal human intervention. \footnote{definition taken from Dictionary.com article 'Bots', retrieved on 2018-07-18.}

\noindent \textbf{ceteris paribus} stands for 'all other things being unchanged or constant'. It is used in economics to rule out the possibility of 'other' factors changing. \footnote{definition taken from Economic Times article 'Freemium', retrieved on 2018-07-18.}

\noindent \textbf{Content-Length} The Content-Length entity-header field indicates the size of the entity-body, in decimal number of OCTETs, sent to the recipient or, in the case of the HEAD method, the size of the entity-body that would have been sent had the request been a GET. \footnote{definition taken from RFC 2616 Fielding, et al., retrieved on 2018-07-18.}

\noindent \textbf{Freemium} is a pricing strategy by which a product or service is provided free of charge, but money (premium) is charged for additional features, services, or virtual (online) or physical (offline) goods. \footnote{definition taken from Wikipedia article 'Freemium', retrieved on 2018-07-18.}

\noindent \textbf{GET} is a HTTP Method used to request data from a specified resource.

\noindent \textbf{n-gram} is a contiguous sequence of n items from a given sample of text or speech. \footnote{definition taken from Wikipedia article 'N-gram', retrieved on 2018-07-18.}

\noindent \textbf{Power Law} states that a relative change in one quantity results in a proportional relative change in another. \footnote{definition taken from Statisticshowto article 'Power Law', retrieved on 2018-07-18.}

\noindent \textbf{POST} is a HTTP Method used to send data to a server to create/update a resource. 

\noindent \textbf{Python} is a programming language

\noindent \textbf{Regex} is a regular expression. In theoretical computer science and formal language theory, it is a sequence of characters that define a search pattern. \footnote{definition taken from Wikipedia article 'Regular Expression', retrieved on 2018-07-18.}

\noindent \textbf{Whitelist} is the practice of identifying entities that are provided a particular privilege, service, mobility, access or recognition. \footnote{definition taken from Wikipedia article 'Whitelisting', retrieved on 2018-07-18.}
